Attributes-based Object Classification and Segmentation

### 2010-05-12 paper.tex
changes

USE SUBTRACTIVE WITH ADDITIVE, FIX SUBTRACTIVE FRAGMENTATION

@@

The holy grail of this approach, of course, is to be able to segment objects
for which the canonical attribute distribution is unknown, based on a measure
of attribute coherence.  If this can be achieved, then segmentation experiments
could open up to non-experts, who could define coherence measures based on
semantic attributes and then could use this approach to automatically segment large
numbers of images even if no detection of their desired object exists.

As object classification is generally only as good as the features used, so also it
appears that this approach to segmentation is only as good as the attribute
selection and training.  We found that in images with poor segmentations, the
confidences in prediction of object-related attributes were generally low. The bounding 
boxes groundtruth can include many background features into the attribute models. Those 
features are very harmful. The extreme example is shown in the left image of figure \ref{fig:horse_bad_results}, 
which only segments out the background grass. However, even if we have the segmentation 
of objects as the groundtruth for training the attributes, we may still not have accurate 
models, since the groundtruth is for objects not for attributes. For example, if we train 
the attributes of wheel or metal only based on car images, we may get the car model not 
the attributes model. One way to deal with this problem is to directly label attributes 
groundtruth. Then we can get similar accurate attribute models as the object models.

Another problem with the attribute based method is that the attributes are not discriminative 
enough to separate different objects. For example, if we use the general attributes of head, torso and leg to 
do the object classification, we cannot separate dog and cat, since both of them have all of the attributes. 
But those attributes can definitely separate the two objects from non-animal objects, such as car. This example demonstrates that 
attributes are helpful for the object classification, but they are not discriminative enough. So one way to deal with this is to use 
both attributes features and low level objects features for object classification. We can train a general attributes models first. 
When we want to classify some specific objects, we can incorporate a small number of low level features from the specific object samples to the attributes 
features. In this way, we both reduce the training samples for object classification, and make the attribute based method more discriminative.

>>>>

@@

As object classification is generally only as good as the features used, so also it
appears that this approach to segmentation is only as good as the attribute
selection and training.  We found that in images with poor segmentations, the
confidences in prediction of object-related attributes were generally low. Using bounding 
boxes as ground truth can introduce many background features into the attribute models. These 
features can be harmful. The extreme example is shown in the left image of figure \ref{fig:horse_bad_results}, 
which only segments out the background grass. However, even if we have the segmentation 
of objects as the ground truth for training the attributes, we may still not have accurate 
models, since the ground truth is for objects not for attributes. For example, if we train 
the attributes of wheel or metal only based on car images, we may get the car model not 
the attributes model. One way to deal with this problem is to directly label attributes 
ground truth. Then we can get similar accurate attribute models as the object models.

Another problem with the attribute based method is that the attributes are not discriminative 
enough to separate different objects. For example, if we use the general attributes of head, torso and leg to 
do the object classification, we cannot separate dog and cat, since both of them have all of the attributes. 
But those attributes can definitely separate the two objects from non-animal objects, such as car. So
attributes are helpful for object classification, but they are often not discriminative enough. One way to deal with this is to use 
both attributes features and low level objects features for object classification. We can train general attributes models first. 
When we want to classify some specific objects, we can incorporate a small number of low level features from the specific object samples to the attributes 
features. In this way, we both reduce the training samples for object classification, and make the attribute based method more discriminative.

Interestingly, the region pruning algorithms are feature-type independent.  That
is, they are not necessarily wedded to attribute features and could be used with
any feature type given a similarity scoring function.  Interesting future work would
be to try the pruning methods with lower-level features.

The holy grail of this approach, of course, is to be able to segment any object
with a given canonical attribute distribution.  If this can be achieved, 
then segmentation experiments
could open up to non-experts, who could define an attribute distribution
based on their own knowledge and use a system that has already been trained
on a large number of attributes to segment the object.
